---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# glyphextra

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/glyphextra)](https://cran.r-project.org/package=glyphextra)
<!-- badges: end -->

The goal of glyphextra is to ...

## Installation

You can install the released version of glyphextra from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("glyphextra")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("EmilHvitfeldt/glyphextra")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ggplot2)
library(glyphextra)

ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  geom_point(key_glyph = draw_key_usa)
```


Please note that the 'glyphextra' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
